Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-03 outputs/paper/paper.qmd
Updated code to graph number of subdivisions per ward

summarized_voter_statistics |>
  kable(
    col.names = c("Ward", "Number of Subdivisions"), 
    booktabs = TRUE
  )
```

@@

summarized_voter_statistics |>
  ggplot(mapping = aes(x = ward, y = n)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Number of Subdivisions per Ward",
    x = "Ward",
    y = "Number of Subdivisions",
  ) +
  theme_classic() +
  scale_fill_brewer(palette = "Set1")

@@

cleaned_voter_statistics |>
  slice(2:52) |>
  count(
    total = max(sub, na.rm = TRUE)
  )

>>>>

head(summarized_voter_statistics, 5) |>
  kable(
    col.names = c("Ward", "Number of Subdivisions"), 
    booktabs = TRUE
  )
```

@@

```{r}
#| message: false
#| echo: false
#| label: fig-voter_statistics
#| tbl-cap: Number of Subdivisions per Ward

#Code refernced from: https://stackoverflow.com/questions/11335836/increase-number-of-axis-ticks
summarized_voter_statistics |>
 ggplot(mapping = aes(x = ward, y = n)) +
  geom_bar(stat = "identity") +
scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
scale_y_continuous(breaks = scales::pretty_breaks(n = 25))+
  labs(
    title = "Number of Subdivisions per Ward",
    x = "Ward",
    y = "Number of Subdivisions",
  ) +
  theme_classic()

@@
